screeningAnalysis

### 2024-03-18 screenCode.Rmd
first draft paper

```{r load data}
#rsq_dat <- read.csv("data/RSQ_Feb06_24.csv") 
rsq_dat <- read.csv("data/RSQ_Feb13_24.csv")

@@

```
```{r}
# Old high RS participants identified in screening in November/December 2023
high_RS_old <- df_screening %>% dplyr::filter(RS_score >= 15, as.Date(ymd_hms(StartDate)) != as.Date("2024-02-06") ) %>% dplyr::select(PROLIFIC_PID)

@@

# Newly identified high RS on the 13th feb 2024.

@@

high_RS_13feb <- df_screening %>% dplyr::filter(RS_score >= 15, as.Date(ymd_hms(StartDate)) == as.Date("2024-02-13") ) %>% dplyr::select(PROLIFIC_PID)

nrow(high_RS_13feb)

# String them together and add to prolific
feb13_ids_string <- paste(high_RS_13feb$PROLIFIC_PID, collapse = ",")

feb13_ids_string
```

>>>>

```{r load data}

#rsq_dat <- read.csv("data/RSQ_Feb15_24.csv") 
rsq_dat <- read.csv("data/RSQ_Feb18_24.csv")

@@

```{r}
# Old high RS participants identified in screening in November/December 2023
high_RS_old <- df_screening %>% dplyr::filter(RS_score >= 15, as.Date(ymd_hms(StartDate)) != as.Date("2024-02-06") ) %>% dplyr::select(PROLIFIC_PID)

@@

# Newly identified high RS on the 18th feb 2024.

@@

high_RS_18feb <- df_screening %>% dplyr::filter(RS_score >= 15, as.Date(ymd_hms(StartDate)) == as.Date("2024-02-18") ) %>% dplyr::select(PROLIFIC_PID)

nrow(high_RS_18feb)

# String them together and add to prolific
feb18_ids_string <- paste(high_RS_18feb$PROLIFIC_PID, collapse = ",")

feb18_ids_string
```
